Viscous Transport in Eroding Porous Media

### 2019-10-15 docs/transport/erosion_transport.tex
modify figs in transport paper

\begin{figure}
\begin{center}
  \includegraphics[height=0.227\textwidth]{./figs/100b_50}
  \includegraphics[height=0.227\textwidth, trim=0cm 0cm 2.8cm 0cm, clip=true]
    {./figs/100b_100}
  \includegraphics[height=0.227\textwidth]{./figs/100b_150}
  \includegraphics[height=0.227\textwidth]{./figs/100b_200}
\end{center}
\caption{\label{fig:Eroding100vort} 100 bodies eroding in a
Hagen-Poiseuille flow. The four snapshots are equispaced in time, and
the color is the fluid vorticity.  Erosion creates many channels
connecting the inlet to the outlet.}
\end{figure}

>>>>

\begin{figure}
%<<<<<<< HEAD
%\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height =0.227\linewidth]{./figs/100b_50}
%\caption{100 bodies, $\phi = 55.54\%$}
%\end{subfigure}%
%\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height =0.227\linewidth]{./figs/100b_100}
%\caption{99 bodies, $\phi = 62.98\%$}
%\end{subfigure}
%\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height =0.227\linewidth]{./figs/100b_150}
%\caption{94 bodies, $\phi = 72.22\%$}
%\end{subfigure}%
%\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height =0.227\linewidth]{./figs/100b_200}
%\caption{82 bodies, $\phi = 83.67\%$}
%\end{subfigure}
\caption{\label{fig:Eroding100vort} The erosion of 100 nearly touching
grains in a Hagen-Poiseuille flow. The four snapshots are evenly spaced
in time, and the color is the fluid vorticity.  Because of the large
number of bodies, erosion creates many channels connecting the inlet to
the outlet.}
%=======
%\begin{center}
 % \includegraphics[height=0.227\textwidth]{./figs/100b_50}
  %\includegraphics[height=0.227\textwidth, trim=0cm 0cm 2.8cm 0cm, clip=true]
 %   {./figs/100b_100}
 % \includegraphics[height=0.227\textwidth]{./figs/100b_150}
 % \includegraphics[height=0.227\textwidth]{./figs/100b_200}
%\end{center}
%\caption{\label{fig:Eroding100vort} 100 bodies eroding in a
%Hagen-Poiseuille flow. The four snapshots are equispaced in time, and
%the color is the fluid vorticity.  Erosion creates many channels
%connecting the inlet to the outlet.}
%>>>>>>> 90934916f4dbe677f0ad6f05331ec1c3515ddab7
\end{figure}
